### 2021-07-22 doc/thesis/chapters/deployment-on-hardware.tex
update
product design

@@

drivers for IPs, libraries to interface with e.g. SD card, etc\\
--> look at software which parts may be interesting to highlight

>>>>

%%%%%%%%%%%%%%%%%%%%
\section{Product Design}

The implemented version of the FM Radio Receiver on the ZedBoard is a working prototype at this point.
The implementation does not support live data streaming.
Instead, antenna data is recorded to a file with the RTL-SDR hardware, using a regular PC.
The antenna data is recorded as IQ data in the baseband.
The file is then stored onto an SD card, that is plugged into the ZedBoard.
The CPU on the SoC then reads it and replays the antenna data to the FPGA.
In the future, this design may be extended to use an embedded Linux operating system.
In that way, the RTL-SDR could be connected to the ZedBoard PCB directly via USB, which would enable a live data stream from the antenna to the FPGA.
However, the chosen solution is sufficient for the aims of this thesis.

@@

The application software is running on a single core of the dual-core ARM Cortex A9 CPU and is built upon a real-time operating system, namely FreeRTOS.
Xilinx provides a ported version of this RTOS with the installation of their software development kit, the Xilinx SDK.
The SDK also includes drivers to support various functionalities, such as support for accessing a FAT file system on the external SD card.
The respective software drivers for the IPs that are used in the FPGA design are automatically imported into the SDK project.
They are embedded in the so-called hardware definition file (HDF) that is generated by Vivado after synthesis, and provided together with the bitstream file.
It is a file with the extension \textit{*.hdf} and can be opened like a regular archive file, with any ZIP archive viewer.

\texttt{--->} look at software which parts may be interesting to highlight
